Figures and tables for paper

### 2023-06-15 analysis/04_figs-tables.Rmd
Renamed final_data

# Load data
results <- read_rds(here("data", "derived_data", "final_data.rds"))
```

@@

mnl_dummy_draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "mnl.rds"))
mnl_index_draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "mnl_index.rds"))

@@

@@

mnl_index_draws %>%
  ggplot(aes(x = beta, y = levels_long)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Attribute Levels")
```

>>>>

# Load data
results <- read_rds(here("data", "derived_data", "data.rds"))
```

@@

mnl_dummy_draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "mnl.rds"))
mnl_index_draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "mnl_index.rds"))
mnl_index_02_draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "mnl_index_02.rds"))

@@

mnl_index_02_draws <- mnl_index_02_draws %>%
  rename(i = l) %>%
  left_join(index_level_lookup, by = "i")

@@

mnl_index_draws %>%
  ggplot(aes(x = beta, y = levels_long)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Attribute Levels")

mnl_index_02_draws %>%
  ggplot(aes(x = beta, y = levels_long)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Attribute Levels")
```
